---
title: "Practical Machine Learning. Course Project"
author: "Fedotov Yury"
date: '17 февраля 2019 г '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading necessary packages
```{r}
library(caret)
# store current working directory and set directory containing data
cwd <- getwd()
```

### Loading data files
```{r}
setwd("C:/User/Fed/R/coursera/ML_project")
traindata <- read.csv("pml-training.csv", na.strings = c("NA", ""))
checkdata <- read.csv("pml-testing.csv", na.strings = c("NA", ""))
```

### Preprocess data
```{r}
#remove columns  containing "NA" data
fullCol<-(colSums(is.na(traindata))==0) & (colSums(is.na(checkdata))==0) | (colnames(traindata)=="classe")
#remove a-priori not  relevant columns
fullCol[1:7]<-rep(FALSE,7)
traindata <- traindata[, fullCol]
checkdata <- checkdata[, fullCol]
```

### Split data
```{r}
set.seed(1) 
inTrain <- createDataPartition(traindata$classe, p = 3/4, list = FALSE)
trainset <- traindata[inTrain, ]
testset <- traindata[-inTrain, ]
trainout <- trainset$classe
trainset$classe<-NULL
```
### Preprocess data using PCA for less computation time of training process and higher model generalisation 
```{r}
res_pca<-prcomp(trainset, scale=TRUE, rank=10)
train_pca<-predict(res_pca, trainset)
test_pca<-predict(res_pca, testset)
ceck_pca<-predict(res_pca, checkdata)
train_pca<-data.frame(train_pca, classe=trainout)
```
### Train different models
```{r}
trCtrl<- trainControl(number = 5)
LDA_Mod <- train(classe~., data=train_pca, method="lda")
RF_Mod <- train(classe~., data=train_pca, method="rf")
GBM_Mod <- train(classe~., data=train_pca, method="gbm", verbose = FALSE)
```
### Compare model performance
```{r}
LDA_Mod$results
RF_Mod$results
GBM_Mod$results

LDA_res<-predict(LDA_Mod, test_pca)
RF_res<-predict(RF_Mod, test_pca)
GBM_res<-predict(GBM_Mod, test_pca)
LDA_cf<-confusionMatrix(LDA_res, testset$classe)
RF_cf<-confusionMatrix(RF_res, testset$classe)
GBM_cf<-confusionMatrix(GBM_res, testset$classe)

LDA_cf$overall[1]
RF_cf$overall[1]
GBM_cf$overall[1]
```
#` Random forest classifier has better overall acuracy
#` Predict samples from testing.csv using Random Forest classifier model
```{r}
predict(RF_Mod, ceck_pca)
```

#restore working directory
setwd(cwd)
```

